On centrality of orthogonal $\Kt$

### 2016-04-25 paper.tex
Minor fix

We can sum up the above discussion into the following result.
\begin{lm} \label{lm:map-iota}
 For a splitting ideal $I\trianglelefteq R$ there exists a well-defined homomorphism 
 $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
 satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. \end{lm}
\begin{proof}
We already know that $\iota$ is well-defined. It suffices to check that the image of $\iota$ is contained in $\St(n,\,R,I)$.
Denote the canonical projection $R\epi R/I$ by $\rho$.
Clearly, the induced group morphism $\rho^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$ sends $X(u,\,v)$ to $X(\rho(u),\,\rho(v))$ and $Y(u,\,v)$ to $Y(\rho(u),\,\rho(v))$. 
Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective, therefore for $x\in\E(n,\,R)e_1$ one has $\rho(x)\in\E(n,\,R/I)e_1$. 
From the additivity relations we get that $X(u,\,0)=1=Y(0,\,v)$, hence $\mathrm{Im}(\iota)\subseteq\Ker(\rho^*)=\St(n,\,R,\,I)$, as required. \end{proof}

>>>>

We can sum up the above discussion into the following result.
\begin{lm} \label{lm:map-iota}
 For any $I \trianglelefteq R$ there exists a well-defined homomorphism $$\iota\colon\St^*(n,\,R,\,I)\rightarrow\St(n,\,R, I) \subseteq \St(n, R)$$ 
 satisfying the equalities $\iota (F(u,\,v)) = X(u,\,v)$ and $\iota (S(u,\,v)) = Y(u,\,v)$. \end{lm}
\begin{proof}
We already know that $\iota$ is well-defined. It suffices to check that the image of $\iota$ is contained in $\St(n,\,R,I)$.
Denote the canonical projection $R\epi R/I$ by $\rho$.
Clearly, the induced group morphism $\rho^*\colon\St(n,\,R)\rightarrow\St(n,\,R/I)$ sends $X(u,\,v)$ to $X(\rho(u),\,\rho(v))$ and $Y(u,\,v)$ to $Y(\rho(u),\,\rho(v))$. 
Observe that $\E(n,\,R)\epi\E(n,\,R/I)$ is surjective, therefore for $x\in\E(n,\,R)e_1$ one has $\rho(x)\in\E(n,\,R/I)e_1$. 
From the additivity relations we get that $X(u,\,0)=1=Y(0,\,v)$, hence $\mathrm{Im}(\iota)\subseteq\Ker(\rho^*)=\St(n,\,R,\,I)$, as required. \end{proof}
